The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-05-13 paper/paper.Rmd
named all chunks

```{r}
# Define competitive distance range
comp_dist <- 7.5

@@

```{r}
# Manually define spatial blocks to act as folds
n_fold <- 4
fold1 <- cbind(c(0, 150, 150, 0), c(300, 300, 450, 450))
fold2 <- cbind(c(150, 300, 300, 150), c(300, 300, 450, 450))
fold3 <- cbind(c(0, 150, 150, 0), c(450, 450, 600, 600))
fold4 <- cbind(c(150, 300, 300, 150), c(450, 450, 600, 600))

@@

```{r, eval = FALSE, echo = FALSE}
# Internal: after removing trees in buffer and have NA for growth, there is one
# tree that is not included in focal_vs_comp_scbi b/c it has no neighbors within
# comp_dist = 7.5m of it
growth_scbi %>% 
  filter(!buffer & !is.na(growth)) %>% 
  filter(!stemID %in% focal_vs_comp_scbi$focal_ID)

@@

```{r, scbi-focal-vs-comp-3}
focal_vs_comp_scbi %>% 
  filter(focal_ID == 4) %>% 
  select(focal_ID, dbh, comp) %>% 
  unnest(cols = "comp")
```

@@

```{r}
comp_bayes_lm_scbi
```

@@

```{r scbi-model-predict}
focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  mutate(growth_hat = predict(comp_bayes_lm_scbi, newdata = focal_vs_comp_scbi))
```
```{r}
focal_vs_comp_scbi %>% 
  select(focal_ID, focal_sp, dbh, growth, growth_hat)
```

@@

focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  mutate(growth_hat_shuffle = predict(comp_bayes_lm_scbi_shuffle, 
                                 newdata = focal_vs_comp_scbi))
```
```{r}
model_rmse_shuffle <- focal_vs_comp_scbi %>%
  rmse(truth = growth, estimate = growth_hat_shuffle) %>%
  pull(.estimate)
model_rmse_shuffle
```

@@

```{r scbi-spatial-cv}
focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  run_cv(comp_dist = comp_dist, blocks = blocks_scbi)
```
```{r}
model_rmse_cv <- focal_vs_comp_scbi %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
model_rmse_cv
```

@@

```{r, eval = FALSE}
library(tidyverse)
library(lubridate)
library(here)
library(sf)
library(viridis)
library(forestecology)
library(blockCV)
library(tictoc)

>>>>

```{r add-buffer}
# Define competitive distance range
comp_dist <- 7.5

@@

```{r manually-define-folds}
# Manually define spatial blocks to act as folds
n_fold <- 4
fold1 <- cbind(c(0, 150, 150, 0), c(300, 300, 450, 450))
fold2 <- cbind(c(150, 300, 300, 150), c(300, 300, 450, 450))
fold3 <- cbind(c(0, 150, 150, 0), c(450, 450, 600, 600))
fold4 <- cbind(c(150, 300, 300, 150), c(450, 450, 600, 600))

@@

```{r internal, eval = FALSE, echo = FALSE}
# Internal: after removing trees in buffer and have NA for growth, there is one
# tree that is not included in focal_vs_comp_scbi b/c it has no neighbors within
# comp_dist = 7.5m of it
growth_scbi %>% 
  filter(!buffer & !is.na(growth)) %>% 
  filter(!stemID %in% focal_vs_comp_scbi$focal_ID)

@@

```{r demonstrate-unnest, scbi-focal-vs-comp-3}
focal_vs_comp_scbi %>% 
  filter(focal_ID == 4) %>% 
  select(focal_ID, dbh, comp) %>% 
  unnest(cols = "comp")
```

@@

```{r show-comp-bayes}
comp_bayes_lm_scbi
```

@@

```{r scbi-model-predict}
focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  mutate(growth_hat = predict(comp_bayes_lm_scbi, newdata = focal_vs_comp_scbi))
```
```{r show-focal-vs-comp}
focal_vs_comp_scbi %>% 
  select(focal_ID, focal_sp, dbh, growth, growth_hat)
```

@@

focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  mutate(growth_hat_shuffle = predict(comp_bayes_lm_scbi_shuffle, 
                                 newdata = focal_vs_comp_scbi))
```
```{r show-rmse-shuffle}
model_rmse_shuffle <- focal_vs_comp_scbi %>%
  rmse(truth = growth, estimate = growth_hat_shuffle) %>%
  pull(.estimate)
model_rmse_shuffle
```

@@

```{r scbi-spatial-cv}
focal_vs_comp_scbi <- focal_vs_comp_scbi %>%
  run_cv(comp_dist = comp_dist, blocks = blocks_scbi)
```
```{r show-rmse-cv}
model_rmse_cv <- focal_vs_comp_scbi %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
model_rmse_cv
```

@@

```{r appendix-code, eval = FALSE, cache = FALSE}
library(tidyverse)
library(lubridate)
library(here)
library(sf)
library(viridis)
library(forestecology)
library(blockCV)
library(tictoc)
